\documentclass{article}
\title{Model for UAV Jamming}
\author{Sean Caver @ Data Machines Corporation}
\begin{document}
\maketitle

This model is cobbled together based on things I found on the web,
things conveyed to me by colleagues at Data Machines, and my own logic
and understanding.  Uncertainty is so noted.

\section{Scenario}

The field of interest is a square in the Euclidean plane.  In this
field, there is a ``source,'' or ``sender,'' labeled $S$, a receiver,
labeled $R$, and $n$ different ``jammers,'' labeled $J_1, \dots, J_n$.
We do not assume that the ability to communicate is symmetric---a
separate calculation is needed when the roles of sender and receiver
are reversed.  Additionally there are $m$ different comms to
facilitate communication.

\section{Optimal Placement Of Comms}

Let $c_i$ denote positions of comms and let $j_k$ denote positions
position of jammers.  If these quantities are known, we can compute
the probability of a successful communication between the headquarters
and an asset (see more details below).  We denote this probability

$$P(\mbox{transmission}|c_i,j_k)$$

Some choices still need to be made about how this probability will be
computed, but it shouldn't be hard.  By total probability,

$$P(\mbox{transmission}|c_i) = \sum_k P(\mbox{transmission}|c_i,j_k)
  P(j_k)$$

It is a sum rather than an integral because we only consider grid
points as possible locations.  That may need to be generalized.  The
second factor of each term in the sum is the posterior probability
already coded for computation and described below.

A final step in the computation is a optimization over the comm
positions $c_i$.

\section{TL;DR}
Let $P_{j}(d_j)$ be the power of jammer $j$ at the receiver, at
distance $d_j$.  Let $P_S(d_S)$ be power of the source at the
receiver, at distance $d_S$.  Let $P_N$ be the power of the ambient
noise.

These functions are given by $P_j = \frac{M_j}{d_j^2}$, for $j = 1,
\dots, n$ and $P_S = \frac{M_S}{d_S^2}$; $P_N$ is a constant.

The probability of a successful transmission is given by

$$\mbox{sigmoid}\left( 10 \log_{10}\left(\frac{P_S(d_S)}{P_1(d_1) +
  P_2(d_2) + \dots + P_n(d_n) + P_N} \right) \right)$$

The quantity in the sigmoid is the strength expressed in decibels, of
the signal against the background that includes all jammers and the
ambient noise, see Equation (1) in reference \cite{parlin2018jamming}

\section{Some thoughts about the man-in-the-middle}
Billy had alerted us to the fact that it was more than just distance
to jammer--jammers in the line of sight were more potent than those
off of it.

I spent a long time trying to justify putting this feature explicitly
in the model.  But the model above seemed most consistent with what I
was reading in the literature and it made sense.  It is distance to
receiver that matters.  A man in the middle generally will jam the
receiver, unless distances are great enough, the ambient noise is
small enough, and the proportionality constant of the jammer is small
enough compared to the proportionality constant of the sender.  This
makes sense to me.

There is such a thing as electomagnetic interferece.  According to
Wikipedia: ``The effect of unwanted energy due to one or a combination
of emissions, radiations, or inductions upon reception in a
radiocommunication system, manifested by any performance degradation,
misinterpretation, or loss of information which could be extracted in
the absence of such unwanted energy.'' My reading of this is this:
interference happens upon the reception of the signal, in the circuits
of a radiocommunication system, not with signal itself.
Electomagnetic waves don't interact, as far as I am aware, but it can
be impossible to pick out the signal in the noise.

Having said all that, a directional receiving antenna would sharpen
the effect of a man-in-the-middle jammer, versus one off to the side,
but for the moment I'm keeping it simple and assuming the antennae
have no preferred direction.  Could change that next, though, by
assuming they are optimally directed to receive the signal in a
particular orientation, and to reject signals in substantially
different directions.

\section{Power}

The power of the radio signal from a point source at a distance $r$ is
given by (assuming the free-space propagation loss model):
$$P_{\mbox{signal}}(d) = \frac{M}{d^2},$$ where $M$ is a
proportionality constant that depends on units, and even with the same
units, can be different for different senders.  Note that $M$ is the
power of the signal at distance 1.  The value of $M$ may be know for
friendlies but need to be extimated for jammers.  Equation (1) in
reference \cite{benner1996effects}, showed a similar equation for
``path loss'' relaxing the free-space propagation loss model with a
proportionality exponent possibly different from 2.  It seems that the
units of distance are important in this model---see reference
\cite{benner1996effects}. I note this observation for the future as I
intend to use the free-space propagation loss model for now.


Equation (5) in reference \cite{xu2007adjusting} gives
$$M = \frac{P_T G_T G_R}{4 \pi},$$ where $P_T$ is the power of the
transmitter, $G_T$ is the gain of the transmitter in the direction of
the receiver, and $G_R$ is the gain of the receiver in the direction
of the transmitter.  Presumably the transmitter could be either the
jammer or the source.  Reference \cite{benner1996effects}, gives a
similar equation that may not be entirely consistent that has a
dependence on wavelength, Equation (1).  The basic thing I get from
this is kind of obvious for anyone raised in the era before cable
television---it depends on the orientation of the anntena how strong
the signal.  Again, I am just putting this observation in this
document for the future.  For the first cut the power received by the
anntena is just a function of the distance to the transmitter, not the
orientation of the antenna.

\section{Jamming}

One reference I have \cite{xu2007adjusting} talks about channel
capacity as the maximum bit rate $S \rightarrow R$, under the
assumption of error correcting codes, etc.  So it seems in this
paradigm that it is not whether you are jammed or not, but how many
bits get through per second.  In several references, including this
one there is a noise term which adds power to the jammer in a
symmetric way.  When the decibels in the equation above drops below
the 0, the channel capacity falls below the bandwidth of the channel.

I am going to ignore the details of channel capacity and error
correcting codes and just say probability of transmission is a
function of the ratio of the powers of signal to background, expressed
as a sigmoid of decibels.

\nocite{*}
\bibliography{jam.bib}
\bibliographystyle{ieeetr}
\end{document}
